---
title: "geospatial"
author: "Ning Hu"
date: "11/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#library(reticulate)
#use_condaenv('r-reticulate',required = TRUE)
```





# R

```{r, include=FALSE}
library(tidyverse)
library(sf)
library(readxl)
library(spData)
library(sp)
library(gridExtra)
library(ggpubr)
```


```{r, include=FALSE}
vote <- read_csv('data/countypres_2000-2016.csv')
vote$FIPS <- as.character(vote$FIPS)
unemp <- read_excel("data/Unemployment.xls",range = cell_limits(c(8, 1), c(NA, NA)))

unemp <- unemp %>%
  select(FIPStxt,Unemployment_rate_2008,Unemployment_rate_2012,Unemployment_rate_2016)

```



```{r, include=FALSE}
## county
county <- st_read('data/tl_2019_us_county-1/tl_2019_us_county.shp')
county <- county %>%
  filter(STATEFP == '06'|STATEFP == 42|STATEFP == 48)

```

# TX
```{r, include=FALSE}
vote_T <- vote %>%
  filter((year==2008|year==2012|year==2016) & party == 'democrat' & state == 'Texas')
vote_T['proportion'] = vote_T['candidatevotes']/vote_T['totalvotes']

vote_T <- vote_T %>%
  left_join(county,by = c('FIPS'='GEOID'))


T11 <- vote_T %>%
  filter(year==2008)
T12 <- vote_T %>%
  filter(year==2012)
T13 <- vote_T %>%
  filter(year==2016)

T11 <- ggplot(T11,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of TX in 2008")

T12 <- ggplot(T12,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of TX in 2012")

T13 <- ggplot(T13,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of TX in 2016")

```

```{r, include=FALSE}
unemp_T <- unemp %>%
  filter(substr(FIPStxt,1,2) == '48') %>%
  left_join(county, by = c('FIPStxt' = 'GEOID')) %>%
  tail(-1)

T21 <- ggplot(unemp_T,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2008))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of TX in 2008")

T22 <- ggplot(unemp_T,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2012))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of TX in 2012")

T23 <- ggplot(unemp_T,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2016))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of TX in 2016")
```

```{r fig1, fig.height = 30, fig.width = 25, fig.align = "center"}
ggarrange(T11,T21,T12,T22,T13,T23,ncol = 2, nrow=3, align = 'hv', widths = c(6,6,6,6,6,6))
```

From the graph we can see that in Texas counties with higher unemployment rate would tend to vote for Democrat candidates.

# CA
```{r, include=FALSE}
vote_C <- vote %>%
  filter((year==2008|year==2012|year==2016) & party == 'democrat' & state == 'California')
vote_C['proportion'] = vote_C['candidatevotes']/vote_C['totalvotes']
vote_C$FIPS <- paste0('0',vote_C$FIPS)
vote_C <- vote_C %>%
  left_join(county,by = c('FIPS'='GEOID'))


C11 <- vote_C %>%
  filter(year==2008)
C12 <- vote_C %>%
  filter(year==2012)
C13 <- vote_C %>%
  filter(year==2016)

C11 <- ggplot(C11,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of CA in 2008")

C12 <- ggplot(C12,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of CA in 2012")

C13 <- ggplot(C13,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of CA in 2016")

```

```{r, include=FALSE}
unemp_C <- unemp %>%
  filter(substr(FIPStxt,1,2) == '06') %>%
  left_join(county, by = c('FIPStxt' = 'GEOID')) %>%
  tail(-1)

C21 <- ggplot(unemp_C,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2008))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of CA in 2008")

C22 <- ggplot(unemp_C,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2012))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of CA in 2012")

C23 <- ggplot(unemp_C,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2016))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of CA in 2016")
```

```{r fig2, fig.height = 30, fig.width = 25, fig.align = "center"}
ggarrange(C11,C21,C12,C22,C13,C23,ncol = 2, nrow=3, align = 'hv', widths = c(6,6,6,6,6,6))
```

In California, most counties with lower unemployment rate would vote for democrat candidates, which is opposite to Texas.

# PA
```{r, include=FALSE}
vote_P <- vote %>%
  filter((year==2008|year==2012|year==2016) & party == 'democrat' & state == 'Pennsylvania')
vote_P['proportion'] = vote_P['candidatevotes']/vote_P['totalvotes']

vote_P <- vote_P %>%
  left_join(county,by = c('FIPS'='GEOID'))


P11 <- vote_P %>%
  filter(year==2008)
P12 <- vote_P %>%
  filter(year==2012)
P13 <- vote_P %>%
  filter(year==2016)

P11 <- ggplot(P11,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of PA in 2008")

P12 <- ggplot(P12,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of PA in 2012")

P13 <- ggplot(P13,aes(geometry=geometry))+
  geom_sf(aes(fill = proportion))+
  scale_fill_distiller(name="Proportion of Votes", palette = "Blues",direction=1)+
  ggtitle("Proportion of Votes for Democrat Candidate of PA in 2016")

```

```{r, include=FALSE}
unemp_P <- unemp %>%
  filter(substr(FIPStxt,1,2) == '42') %>%
  left_join(county, by = c('FIPStxt' = 'GEOID')) %>%
  tail(-1)

P21 <- ggplot(unemp_P,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2008))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of PA in 2008")

P22 <- ggplot(unemp_P,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2012))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of PA in 2012")

P23 <- ggplot(unemp_P,aes(geometry=geometry))+
  geom_sf(aes(fill = Unemployment_rate_2016))+
  scale_fill_distiller(name="Unemployment rate", palette = "Reds",direction=1)+
  ggtitle("Unemployment rate of PA in 2016")
```

```{r fig3, fig.height = 30, fig.width = 25, fig.align = "center"}
ggarrange(P11,P21,P12,P22,P13,P23,ncol = 2, nrow=3, align = 'hv', widths = c(6,6,6,6,6,6))
```

Counties with lower unemployment rate would tend to have a higher proportion of vote for Democrat candidate in PA.





